---
title: "Survival for Reconstructed"
author: "Ahmed Shaheen"
date: "2022-08-30"
output: html_document
---

#Loading libraries
```{r}
library(survival)
library(tidyverse)
library(janitor)
library(readxl)
library(survminer)
```


#Loading data
```{r}
data = read_excel('~/Downloads/Meta of KM (PFA)/Reconstructed/Reconstructed data.xlsx') %>% mutate_if(is.character, ~as.factor(as.character(.)))
```


#Building a Survival Object
```{r}
surv <- Surv(time = data$time, event = data$status)
```


#Median survival time
```{r}
fita <- survfit(surv ~ 1)
print(fita)
```


```{r}

fitc <- survfit(surv ~ data$treat)
print(fitc)
```


#Testing the difference between two survival curves
```{r}
survdiff(surv ~ data$treat)
```

jpeg(file="~/Downloads/Meta of KM (PFA)/Results/Survival plot all.jpeg")
dev.off()

#K-M Plot with a number at risk table
```{r}

#jpeg(file="~/Downloads/Meta of KM (PFA)/Results/Survival plot all.jpeg")

ggsurvplot(fitc, data = data, size = 1,
   palette = c("purple", "darkgoldenrod"), 
   conf.int = TRUE, 
   pval = TRUE, 
   risk.table = TRUE, 
   risk.table.height = 0.25, 
   risk.table.y.text.col = T, 
   xlab = "Time in Days", 
   break.time.by = 500,
   legend.labs = c("Endo", "Endo-Epicardial"), 
   ggtheme = theme_bw() 
   )
#dev.off()

ggsurvplot(fita, data = data,size = 1,
   conf.int = TRUE, 
   risk.table = TRUE, 
   risk.table.height = 0.25,
   xlab = "Time in Days",
   ggtheme = theme_bw() ,
   break.time.by = 500
)
```


#Cumulative hazard function
```{r}
fit33 <- survfit(Surv(time, status) ~ treat, data = data)
ggsurvplot(fit33, data,
          conf.int = TRUE,
          risk.table.col = "strata", 
          ggtheme = theme_bw(), 
          palette = c("#E7B800", "#2E9FDF"),
          fun = "cumhaz")

```


#Conditional survival over all data
```{r}
# plot the conditional survival curves at baseline, and for those who have survived 0:10 years
library(condsurv)
data$os_yrs = data$time/(30*12)
myfit <- survfit(Surv(os_yrs, status) ~ 1, data = data)

cond_times <- seq(0, 10, 1)

gg_conditional_surv(
  basekm = myfit, 
  at = cond_times,
  xlab = "Years",
  main = "Conditional survival: all"
  ) +
  labs(color = "Conditional Time")

#conditional survival estimate of surviving to a variety of different time points given that the subject has already survived for 0 years
prob_times <- seq(0, 10, 1)

purrr::map_df(
  prob_times, 
  ~conditional_surv_est(
    basekm = myfit, 
    t1 = 0, 
    t2 = .x) 
  ) %>% 
  mutate(years = prob_times) %>% 
  select(years, everything()) %>% 
  knitr::kable()
```


#Conditional survival in endo alone
```{r}
datae <- as_tibble(data)
datae = datae  %>% filter(treat == "Endo")

# plot the conditional survival curves at baseline, and for those who have survived 0:10 years

datae$os_yrs = datae$time/(30*12)
myfit <- survfit(Surv(os_yrs, status) ~ 1, data = datae)

cond_times <- seq(0, 10, 1)

gg_conditional_surv(
  basekm = myfit, 
  at = cond_times,
  xlab = "Years",
  main = "Conditional survival: Endo"
  ) +
  labs(color = "Conditional Time")

#conditional survival estimate of surviving to a variety of different time points given that the subject has already survived for 0 years
prob_times <- seq(0, 10, 1)

purrr::map_df(
  prob_times, 
  ~conditional_surv_est(
    basekm = myfit, 
    t1 = 0, 
    t2 = .x) 
  ) %>% 
  mutate(years = prob_times) %>% 
  select(years, everything()) %>% 
  knitr::kable()
```





#Conditional survival in endo/epi group
```{r}

datai <- as_tibble(data)
datai = datai  %>% filter(treat == "Endo-epicardial")
# plot the conditional survival curves at baseline, and for those who have survived 0:10 years

datai$os_yrs = datai$time/(30*12)
myfit <- survfit(Surv(os_yrs, status) ~ 1, data = datai)

cond_times <- seq(0, 10, 1)

gg_conditional_surv(
  basekm = myfit, 
  at = cond_times,
  xlab = "Years",
  main = "Conditional survival: Endo-epicardial"
  ) +
  labs(color = "Conditional Time")

#conditional survival estimate of surviving to a variety of different time points given that the subject has already survived for 0 years
prob_times <- seq(0, 10, 1)

purrr::map_df(
  prob_times, 
  ~conditional_surv_est(
    basekm = myfit, 
    t1 = 0, 
    t2 = .x) 
  ) %>% 
  mutate(years = prob_times) %>% 
  select(years, everything()) %>% 
  knitr::kable()
```



#Cox Regression Model assumption 
```{r}
mv_fit <- coxph(Surv(time, status) ~ treat, data = data)
cz <- cox.zph(mv_fit)
print(cz)
plot(cz)
ggcoxzph(cz)
```

```{r}
summary(mv_fit)
```

```{r}
library(broom)
tidy(mv_fit, exponentiate = TRUE)
```
```{r}
Publish::publish(mv_fit)
```


```{r}
anova(mv_fit)
```


#Fitting a Cox Model using cph from the rms package
```{r}
library(rms)
units(data$time) <- "Days"
d <- datadist(data)
options(datadist = "d")

hemsurv <- Surv(time = data$time, event = data$status)

model_hem <- cph(hemsurv ~ treat, data = data, 
                 x = TRUE, y = TRUE, surv = TRUE)
```


```{r}
plot(summary(model_hem),main = "")
title(main = "Hazard Ratio",line = 1.1, adj =0.65)
```


#Treatment’s effect on log relative hazard
```{r}
ggplot(Predict(model_hem, treat))
```


#nomogram
```{r}
survx <- Survival(model_hem)
plot(nomogram(model_hem, fun=list(function(x) survx(365, x),
                                  function(x) survx(365*2, x),
                                  function(x) survx(365*3, x),
                                  function(x) survx(365*10, x)),
                                  funlabel=c("One-Year Pr(Survival)", 
                                             "Two-Year Pr(Survival)",
                                             "Three-Year Pr(Survival)",
                                             "Ten-Years Pr(Survival)")))
```




#Landmark approach
### Step 1 Select landmark time
### Step 2 Subset population for those followed at least until landmark time
###Step 3 Calculate follow-up time from landmark and apply traditional methods.


```{r}
lm_dat <- 
  data %>% 
  filter(time >= 1000) 
```


```{r}
lm_dat <- 
  lm_dat %>% 
  mutate(
    lm_T1 = time - 1000
    )
```

We exclude 800 patients who were not followed until the landmark time of 90 days


```{r}

surv <- Surv(time = lm_dat$lm_T1, event = lm_dat$status)
fit <- survfit(surv ~ lm_dat$treat)
  ggsurvplot(fit, data = lm_dat, size = 1,
      palette = c("purple", "darkgoldenrod"), 
      conf.int = TRUE, 
      pval = TRUE, 
      risk.table = TRUE, 
      risk.table.height = 0.25, 
      risk.table.y.text.col = T, 
      xlab = "Days from 1000-day landmark", 
      break.time.by = 500,
      legend.labs = c("Endo", "Endo-Epicardial"), 
      ggtheme = theme_bw() )
```


```{r}
library(gtsummary)
library(survival)
coxph(
  Surv(time, status) ~ treat, 
  subset = time >= 1000, 
  data = data
  ) %>% 
  tbl_regression(exp = TRUE)
```



#Sensitivity Analysis ( For each subtype of the diseases)

```{r}
groups = levels(data$group)
group_name <- list()
HR <- list()  
seHR <- list() 
P_value <- list()
for(i in groups ) {                                           
  datag <- data  %>% filter(group == i) 
  fit <- coxph(Surv(time, status) ~ treat, data = datag)          
  sumfit <-summary(fit)  
  sumfit <- as.data.frame(sumfit$coefficients)
  group_name <- append(group_name, i)
  HR <-  append(HR,c(sumfit$`exp(coef)`))
  seHR <- append(seHR,c(sumfit$`se(coef)`)) 
  P_value <- append(P_value,c(sumfit$`Pr(>|z|)`)) 
}

hazardratios = data.frame(unlist(group_name),unlist(HR), unlist(seHR), unlist(P_value)) %>% clean_names()

```


```{r}
hazardratios <- as_tibble(hazardratios)
hazardratios <- hazardratios %>% rename( Disease = unlist_group_name,
                         'HR of the combined therapy' = unlist_hr ,
                         'standard error' = unlist_se_hr,
                         P.value = unlist_p_value )

hazardratios

```




```{r}

for(i in groups ) {                                           
   datag <- data  %>% filter(group == i) 
   surv <- Surv(time = datag$time, event = datag$status)

   fit <- survfit(surv ~ datag$treat)
  
   
   plot <- ggsurvplot(fit, data = datag, size = 1,
      palette = c("purple", "darkgoldenrod"), 
      conf.int = TRUE, 
      pval = TRUE, 
      risk.table = TRUE, 
      risk.table.height = 0.25, 
      risk.table.y.text.col = T, 
      xlab = "Time in Days", 
      break.time.by = 500,
      legend.title = i ,
      legend.labs = c("Endo", "Endo-Epicardial"), 
      ggtheme = theme_bw() )
   print(plot)
  
}


```




#Heterogniety 
```{r}
studies = levels(data$study)
study_names <- list()
HR <- list()  
seHR <- list() 
for(i in studies ) {                                           
  datag <- data  %>% filter(study == i) 
  fit <- coxph(Surv(time, status) ~ treat, data = datag)                        
  sumfit <- summary(fit)  
  sumfit <- as.data.frame(sumfit$coefficients)
  study_names <- append(study_names, i)
  HR <-  append(HR,c(sumfit$`exp(coef)`))
  seHR <- append(seHR,c(sumfit$`se(coef)`))
}

hazardperstudy = data.frame(unlist(study_names),unlist(HR), unlist(seHR)) %>% clean_names()
```



```{r}
library(meta)
library(metafor)
madata <- metagen(TE = unlist_hr,
            seTE = unlist_se_hr,
            data = hazardperstudy,
            studlab = paste(unlist_study_names),
            fixed = TRUE,
            random = TRUE,
            method.tau = "DL",
            hakn = FALSE,
            prediction = TRUE)
forest(madata,fontsize = 8)
```

